---
title: "Melvin's Storyboard"
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    storyboard: true
    self_contained: true

---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(skimr)
library(inspectdf)
library(palmerpenguins)
library(ggthemes)
# create www folder
fs::dir_create("www/")
# options for chunks
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  collapse = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  dev = "ragg_png",
  out.width = '85%',
  fig.path = "www/",
  dpi = 320,
  fig.align = "center",
  fig.width = 7,
  fig.height = 5.5,
  fig.retina = 2
  )
# tibble printing
options(
  pillar.print_max = 10, 
  pillar.print_min = 10)
```


### Cannabis History {data-commentary-width=350}

The data depicted in these datasets come from Kushy App, an open source application and data for the cannabis industry. It records and gauges the popularity of cannabis products, strains and brands. More information about the data can be found at https://github.com/kushyapp/cannabis-dataset

```{r import, echo=FALSE}
brands_raw <- readr::read_csv('data/raw/brand_raw.csv')
strains_raw <- read_csv("data/strains_null_na.csv", 
    na = "NA")
products_raw <- readr::read_csv('data/raw/products_csv')
top_cat <- brands_raw %>% 
  count(category, sort = TRUE) %>%
  filter(!is.na(category)) %>% 
  head(25)

```


*** 

Additional links or sources...

### Cannabis Brands {data-commentary-width=400}

```{r, echo=FALSE} 
labs_bar <- labs(
  title = "Top 25 Cannabis Categories",
  x = "count", y = "category")

ggp2_bar <- ggplot(data = top_cat,
     aes(x = n, y = forcats::fct_reorder(category, n))) + 
     geom_col(aes(fill= category), show.legend = FALSE, stat="count") +
     ggthemes::theme_gdocs(base_size = 8)
ggp2_bar + 
  labs_bar

```


*** 

```{r, eval= FALSE} 
labs_bar <- labs(
  title = "Top 25 Cannabis Categories",
  x = "count", y = "category")

ggp2_bar <- ggplot(data = top_cat,
     aes(x = n, 
         y = forcats::fct_reorder(
           category, n))) + 
     geom_col(aes(fill= category), 
              show.legend = FALSE, 
              stat="count") 
ggp2_bar + 
  labs_bar

```

### Cannabis Strains {data-commentary-width=400}


``` {r col, echo = FALSE}
labs_col <- labs(
  title = "Top Cannabis Flavors",
  x = "count", y = "flavor", 
  fill = "flavor")
strains_raw %>% 
  filter(!is.na(flavor)) %>% 
  count(flavor, sort= TRUE) %>%
  head(20) %>% 
 ggplot(data = ., 
       aes(x = n, 
           y = fct_reorder(
             .f = as.factor(flavor), 
             .x = n))) + 
    geom_col(aes(fill = flavor), 
        show.legend = FALSE) +
ggthemes::theme_gdocs(base_size = 8) -> ggp2_col 

ggp2_col + labs_col
```


***

``` {r col_hide, eval = FALSE}
labs_col <- labs(
  title = "Top Cannabis Flavors",
  x = "count", y = "flavor", 
  fill = "flavor")
strains_raw %>% 
  filter(!is.na(flavor)) %>% 
  count(flavor, sort= TRUE) %>%
  head(20) %>% 
 ggplot(data = ., 
       aes(x = n, 
           y = fct_reorder(
             .f = as.factor(flavor), 
             .x = n))) + 
    geom_col(aes(fill = flavor), 
             show.legend = FALSE) -> ggp2_col
ggp2_col + labs_col
```

### Cannabis Products {data-commentary-width=400}
 



```{r echo= FALSE} 
labs_bar <- labs(
  title = "Cannabis Products",
  x = "count", y = "brand", 
  fill = "brand")
products_raw %>% 
  count(brand, sort= TRUE) %>%
  head(20) %>% 
  ggplot(data = ., 
       aes(x = n, y = fct_reorder(.f = as.factor(brand), .x = n))) + 
    geom_col(aes(fill = brand), 
             show.legend = FALSE) +
ggthemes::theme_gdocs(base_size = 8) -> ggp2_bar 
ggp2_bar + 
  labs_bar
  
```


*** 

```{r eval= FALSE} 
labs_bar <- labs(title = "Cannabis Products",
                 x = "count",
                 y = "brand",
                 fill = "brand")
products_raw %>%
  count(brand, sort = TRUE) %>%
  head(20) %>%
  ggplot(data = .,
         aes(x = n, 
             y = fct_reorder(
               .f = as.factor(brand), 
               .x = n))) +
  geom_col(aes(fill = brand),
           show.legend = FALSE) -> ggp2_bar
ggp2_bar +
  labs_bar

```